Reducing retrieval error in MAIAC AOD with the `Earth_obs_cleaning` machine-learning workflow: Results from CONUS

### 2023-08-26 writing/CONUS_AOD.qmd
Minor typos.

The study region was the conterminous United States (CONUS) and all match-ups of MODIS data were based on the 1 km grid cells in the Global sinusoidal Coordinate Reference System. The study period included all retrievals from `r min(Wf$dates)` through `r max(Wf$dates)`. The `Earth_obs_cleaning` workflow automatically downloaded all intersecting tiles of MCD19A2 Collection 6.1[@lyapustinalexei2018] based on a NASA-supplied MODIS tile boundary file. While the MCD19A2 product includes data from both Aqua and Terra MODIS instruments, we focus our analyses on the longer running Terra.

@@

After cross validation, the model was refit with the entire training data set and predictions were generated to correct AOD in new locations (i.e., grid cells without AERONET sites) on demand. The `Earth_obs_cleaning` workflow stores these in Parquet format for efficient data storage and retrieval. To demonstrate that corrected AOD still shows spatial patterns consistent with expectations we generated maps of raw and corrected MAIAC on a typical day (selected as the tile with the most non-missing AOD on the day with the median improvement in MSE for AERONET stations). To show the correction in known high-AOD conditions we plotted the Baltimore, MA area on June 10, 2015 which had substantial subsiding long-range transported Canadian wildfire smoke as previously documented with extensive surface and atmospheric monitoring [@dreessen2016].

>>>>

The study region was the conterminous United States (CONUS) and all match-ups of MODIS data were based on the 1 km grid cells in the Global sinusoidal Coordinate Reference System. The study period included all retrievals from `r min(Wf$dates)` through `r max(Wf$dates)`. The `Earth_obs_cleaning` workflow automatically downloaded all intersecting tiles of MCD19A2 Collection 6.1 [@lyapustinalexei2018] based on a NASA-supplied MODIS tile boundary file. While the MCD19A2 product includes data from both Aqua and Terra MODIS instruments, we focus our analyses on the longer running Terra.

@@

After cross validation, the model was refit with the entire training data set and predictions were generated to correct AOD in new locations (i.e., grid cells without AERONET sites) on demand. The `Earth_obs_cleaning` workflow stores these in Parquet format for efficient data storage and retrieval. To demonstrate that corrected AOD still shows spatial patterns consistent with expectations we generated maps of raw and corrected MAIAC on a typical day (selected as the tile with the most non-missing AOD on the day with the median improvement in MSE for AERONET stations). To show the correction in known high-AOD conditions we plotted the Baltimore, MD area on June 10, 2015 which had substantial subsiding long-range transported Canadian wildfire smoke as previously documented with extensive surface and atmospheric monitoring [@dreessen2016].
